### 2022-01-26 input/abstract.tex
finalize abstract comment
final abstract

  %% \NAME is a crazy contribution
  \noindent As such, \NAME can constitute a novel building block for
  geo-distributed services, \eg by efficiently sharing the locations
  of replicated web objects in the vicinity of downloading \processes, \note{vicinity redundant + see tex}
  %ici on perd la notion que les autres noeuds en périphérie peuvent en beneficier + redondance sur vicinity
  or by enabling efficient resource discovery in the vicinity of a
  region.

>>>>

  %% \NAME is a crazy contribution
  \noindent As such, \NAME can constitute a novel building block for
  geo-distributed services, \eg by efficiently sharing the locations
  of replicated web objects
  to allow nodes benefit from neighborhood downloads
  %in the vicinity of downloading \processes, \note{vicinity redundant + see tex}
  %ici on perd la notion que les autres noeuds en périphérie peuvent en beneficier (to allow nodes benefit from neighborhood downloads) + redondance sur vicinit:
  or by enabling efficient resource discovery in the vicinity of a
  region.
